Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-08-17 paper/manuscript.tex
first complete draft of discussion

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{social cognition, individual differences, gaze cues, psychometrics\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
  pdflang={en-EN},
  pdfkeywords={social cognition, individual differences, gaze cues, psychometrics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016).
This might be because traditional measures of social cognition are not designed to capture variation between children:
they often rely on low trial numbers, small sample sizes, and dichotomous measures. A recent review showed that many atudies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).

@@

Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
Another goal in creating new tasks should be to focus on ``face value'':
measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes:
gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent --
and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
In our definition, gaze understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects. Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.~The landing of the target is accompanied by a tapping sound. Once the target landed, the instructor's voice asks ``Where is the balloon?''. For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice. If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample. Furthermore, we were interested in how the data collection mode influences responses.

@@

For our remote child sample, we recruited families via an internal database. The remote child sample included 147 children, including
45 3-year-olds
(mean = 42.62 months,
SD = 3.35,
range = 36
- 47,
14 girls),
47 4-year-olds
(mean = 52.64 months,
SD = 3.40,
range = 48
- 59,
25 girls),
and 55 5-year-olds
(mean = 65.11 months,
SD = 3.77,
range = 60
- 71,
27 girls). Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018). \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of 100 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

\caption{\textbf{Measuring inter-individual variation}.
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
Small points show the mean performance for each subject averaged across trials. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection. Color of data points denotes age group.}\label{fig:fig2}
\end{figure}

We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target. In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F). Most participants in the box version performed above chance level. By the end of their sixth year of life, children came close to the adult's proficiency level. Most importantly, however, we found substantial inter-individual variation across study versions and age groups. For example, some three-year-olds were more precise in their responses than some five-year-olds. Even though variation is smaller, we even find inter-individual differences in the adult sample.

@@

Our task induced inter-individual variation in both adults and children. We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target. The five-year-olds reached a proficiency level close to the adults' level. For neither study version nor age group did we find any floor or ceiling effects. The presentation as a tablet game kept children interest and motivated throughout the 15 test trials. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This illustrates the flexibility of the task.

@@

As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable. We assessed internal consistency (split-half reliability) and test-retest reliability. Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for child sample, and \url{https://osf.io/nu62m} adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between July 2021 and April 2022.

@@

The adult sample consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).

@@

We assessed reliability in two ways. First, we focused on the internal consistency by calculating splithalf reliability coefficients. For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using \emph{Pearson} coefficients. For this, we used the data of the first test day. Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design. To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position. First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling. Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).

Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019). We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function. The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates. Most importantly, the model includes age as a fixed effect. The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences. A high correlation between our participant specific model estimates would speak for a high association between test days.

@@

The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.90 (95\% CI {[}0.67;1.00{]}).
In the box version it was 0.91 (95\% CI {[}0.69;1.00{]}).

@@

In this paper, we presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
This paper contributes to methodological advances in developmental psychology in the following ways.
First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
Second, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
Finally, we found that gaze understanding relates to aspects of children's everyday experience.
The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are openly accessible.
We want to highlight that researchers are welcome to use and modify our task according to their needs.

One of the main contributions of this paper is that our newly presented gaze understanding task induces variation between participants.
This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
Our experimental design enables a continuous outcome measure, which again quantifies individual differences.

In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
The outcome measure depends on the presented study version:
in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
Both study versions exhibit high retest reliability.
Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates {[}cf. Hughes et al. (2000); improved reliability through aggregation{]}.
When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children. In addition, researchers could induce different levels of salience for each box. Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature of the agent).
In sum, our task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.

In addition to the new task design itself, we designed a new testing infrastructure.
Our gaze understanding task is presented as an interactive web app.
This enables presentation across devices without any prior installation.
Stimuli presentation is achieved through the use of SVGs. This has several advantages:
the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
The cartoon-like presentation makes the task engaging for children and adults alike.

Participants can be tested in-person with supervision or remotely at home.
Test instructions are standardized and, with prior informed consent, the webcam records study participation.
This allows us to scale up data collection: testing is flexible, fast and requires no further experimenter training.
We compared children participating in-person, supervised in kindergartens with children participated remotely at home.
Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
Children in the remote sample are slightly more precise.
This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Appendix XXX).
Therefore, we recommend using a tablet for remote data collection.
Children can then click for themselves and caregivers have less chance to interfere.

\hypertarget{todo-adjust-discussion-part-validity}{%
\section{TODO adjust discussion part validity}\label{todo-adjust-discussion-part-validity}}

Validity is often assessed by looking at concurrent relations between measures. Here we looked at a relation that is often postulated for social cognition tasks, namely that social-cognitive ability is predicted by family level variables.
We found that children's gaze understanding relates to factors of their social environment:
children were more accurate, the more social exposure and the more diverse their surrounding was.
However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items.
We hope that future technological advances will enable continuous measures of children's real life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).

\hypertarget{future-research}{%
\subsection{Future research}\label{future-research}}

Even though aggregate scores seem to improve reliability estimates (cf. Hughes et al., 2000), they may smooth out noise that could be attributed to individual differences.
As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
A potentially promising approach are computational cognitive models.
We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and interpretable manner.
Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks. With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).

Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center). By inducing more between-person variance, reliability estimates could further increase.

Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
We aim at creating a task battery to study individual differences in various aspects of social cognition.
As Schaafsma et al. (2015) pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries. We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.

\hypertarget{limitations}{%
\section{Limitations}\label{limitations}}

@@

\begin{itemize}
\tightlist
\item
  big picture
\item
  ind diff important for \ldots, good measures needed
\item
  dedicated measures of ind diff instead of simply using well-established. reliability paradox paper zitieren
\item
  task \& infrastructure
\item
  foundations for more precise measures for cognitive development
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding.
The task is presented as an interactive web app that does not require any prior installation and works across devices.
Data collection is enabled at scale, with supervised and remote testing and standardized test instructions.
Stimuli presentation is achieved through the use of SVGs which has several advantages:
the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
  pdflang={en-EN},
  pdfkeywords={social cognition, individual differences, gaze cues, cognitive development},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016). This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures. A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).

@@

Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
In our definition, gaze understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asks ``Where is the balloon?''.
For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
Participants do not receive differential feedback so that learning effects are reduced and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.

@@

For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in studies on child development and who indicated interest in online studies.
Families received an email with a short study description and a personalized link, and received a reminder two weeks later if they had not already participated in the study.

The remote child sample included 147 children, including 45 3-year-olds (mean = 42.62 months, SD = 3.35, range = 36 - 47, 14 girls), 47 4-year-olds (mean = 52.64 months, SD = 3.40, range = 48 - 59, 25 girls), and 55 5-year-olds (mean = 65.11 months, SD = 3.77, range = 60 - 71, 27 girls).
Children in our sample grow up in an industrialized, urban Central-European context.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

\caption{\textbf{Measuring inter-individual variation}. (A) Developmental trajectory in continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95\% CrI) based on GLMMs, with the line type indicating the data collection mode. For (B-E) and (G-J), regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}. Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection. Color of data points denotes age group.}\label{fig:fig2}
\end{figure}

We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
Most participants in the box version performed above chance level.
By the end of their sixth year of life, children came close to the adult's proficiency level.
Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
For example, some three-year-olds were more precise in their responses than some five-year-olds.
Even though variation is smaller, we could even find inter-individual differences in the adult sample.

@@

Our task induced inter-individual variation in both children and adults.
We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
The five-year-olds reached a proficiency level close to the adults' level.
For neither study version nor age group did we find any floor or ceiling effects.
The presentation as a tablet game kept children interest and motivated throughout the 15 test trials.
Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
This illustrates the flexibility of the task design.

@@

As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
We assessed internal consistency (as splithalf reliability) and test-retest reliability.
Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for the child sample, and \url{https://osf.io/nu62m} for the adult sample).
Participants were equally distributed across the two study versions.
The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
Data was collected between July 2021 and June 2022.

@@

The adult sample consisted of 136 English-speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females).

@@

We assessed reliability in two ways.
First, we focused on the internal consistency by calculating splithalf reliability coefficients.
For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using \emph{Pearson} coefficients.
For this, we used the data of the first test day.
Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing splithalf reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).

Second, we assessed the test-retest reliability.
We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
The model computes a correlation between the participant-specific estimates for each test day.
This can be interpreted as the test-retest reliability.
By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates.
Most importantly, the model includes age as a fixed effect.
The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
A high correlation between our participant specific model estimates would speak for a high association between test days.

@@

The age-corrected, GLMM based retest reliabilities for children yielded similar results.
In the hedge version, the correlation between testdays was 0.90 (95\% CI {[}0.67;1.00{]}).
In the box version, the correlation between testdays was 0.91 (95\% CI {[}0.69;1.00{]}).

@@

We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
This paper contributes to methodological advances in developmental psychology in the following ways.
First, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
Individuals behaved consistently different from one another.
Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
In sum, our gaze understanding task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are freely accessible.
We want to highlight that researchers are welcome to use and modify our task according to their needs.

One of the main contributions of the gaze understanding task is that it induces variation between participants.
This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).

In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
The outcome measure depends on the presented study version: in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.

Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) towards an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building (Hedge et al., 2018).

Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
Both study versions exhibit high retest reliability, also when controlling for age.
Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al. (2000); improved reliability through aggregation).
When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature/behavioral characteristic of the agent).

Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
Another task extension could realize differential feedback dependent on the participant's accuracy.
By inducing more between-person variance, reliability estimates could further increase.

As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
A potentially promising approach are computational cognitive models.
We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022)

In addition to the new task design itself, we designed a new testing infrastructure.
Our gaze understanding task is presented as an interactive web app.
This enables presentation across devices without any prior installation.
Stimuli presentation is achieved through the use of SVGs.
This has several advantages: the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
The cartoon-like presentation makes the task engaging for children and adults alike.
Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.

The web-based implementation allows for different data collection modes: participants can be tested in-person with supervision or remotely at home.
Test instructions are standardized and, with prior informed consent, the webcam records study participation.
This allows us to scale up data collection: testing is flexible, fast and requires no further experimenter training.
We compared children participating in-person, supervised in kindergartens with children participated remotely at home.
Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
Children in the remote sample are slightly more precise.
This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
Therefore, we recommend using a tablet for remote data collection.
Children can click for themselves and caregivers have less chance to interfere.

The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.

After having proven satisfactory psychometric properties, the next step will be to ensure the validity of our task.
Validity is often assessed by looking at concurrent relations between measures.
Studies on gaze following traditionally present children with a simultaneous, congruent movement of eyes and head orientation.
In our study, however, children only observe a subtle eye movement.
Therefore, our results are not directly comparable to traditional gaze following studies.
Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
In addition, a subset of our remote child sample completed a receptive vocabulary task (Bohn, Prein, Delikaya, Haun, \& Gagarina, n.d.). We will report the association between these family-level factors and children's language on their gaze understanding abilities in a separate paper (in preparation). In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).

Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
As has been pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.

@@

We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in-person.
Ultimately, this work shows a promising way forward towards more precise measures of cognitive development.
The dataset and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
A demo version of the task is available at the following website: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: \url{https://github.com/ccp-eva/gafo-demo}.
These resources allow interested researchers to use, extend and adapt the task.
